---
title: "introductions"
author: "Sunny Sun"
date: "12/2/2018"
output: html_document
vignette: >
  %\VignetteIndexEntry{Introduction to roller}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(roller)
```

## Roller

The package `"roller"` is a minimal implementation for simulating rolling
a die a given number of times, and to visualize the relative frequencies
in such a series of rolls.


## Creating a `roll`

The first step is to create a `"roll"` object with the function `roll()`:

```{r}
myroll <- roll()
myroll
```

By default, `roll()` creates a _fair_ roll with standard sides `1`, and 
`2`, and with probability values for each side of 0.5.

You can change the defatuls with arguments `sides` and `prob`:

```{r}
loaded <- roll(sides = c('1', '2'), prob = c(0.8, 0.2))
loaded
```


## Rolling a die

Once you have defined a `"roll"` object, you can use the function `roll()` to
_roll_ a coin a given number of `times`. The output will be an object of class 
`"roll"`, which will contain the vector of `roll`:

```{r}
roll100 <- roll(myroll, times = 100)
roll100
```

The `summary()` function gives you a nice table of frequencies:
```{r}
summary(roll100)
```


## Plot of relative frequencies

You can use the function `plot()` to create a graohic with the relative 
frequencies of a series of coin tosses:

```{r, fig.show='hold'}
plot.roll(toss100)
```